Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-12 TEBenchmarkPaper/article.tex
Update total runtime estimate

To determine our benchmarking parameters we ran some initial tests on both tools
for samples sized between 1 and 100, for an hour each. Most QuickSpec runs
either finished within 200 seconds or not at all, and sizes above 20 mostly
timed out. IsaCoSy mostly finished within 300 seconds on sample sizes up to 4,
but by size 8 was mostly timing out; its few successes above this took thousands
of seconds each, which we deemed infeasibly long.

We decided to benchmark sample sizes up to 20, since neither tool seemed to
perform well beyond this, and we followed the statistical ``rule of thumb'' of
picking 30 samples for each size\footnote{Only 29 samples of size 2 were
  analysed since one was a duplicate, due to the constraint that samples contain
  at least one theorem's dependencies.}. This gave $20$ sizes $\times 30$
samples $\times 2$ tools $= 1200$ runs. To keep the total time down to a few
days we chose a timeout of 300 seconds, since that covered most of the
successful QuickSpec and IsaCoSy results we saw, and longer times gave rapidly
diminishing returns.

>>>>

To determine our benchmarking parameters we ran some initial tests on both tools
for a few samples sized between 1 and 100, for an hour each. Most QuickSpec runs
either finished within 200 seconds or not at all, and sizes above 20 mostly
timed out. IsaCoSy mostly finished within 300 seconds on sample sizes up to 4,
but by size 8 was mostly timing out; its few successes above this took thousands
of seconds each, which we deemed infeasibly long.

We decided to benchmark sample sizes up to 20, since neither tool seemed to
perform well beyond this. Our results will be analysed by Speedup-test protocol,
which follows the statistical ``rule of thumb'' of treating sample sizes
$\leq$ 30 as ``small'', so we pick 31 samples of each size in order to cross
this (arbitrary) threshold\footnote{Only 14 samples of size 1 were analysed, and
  30 of size 2, since the rest were duplicates. This is due to the constraint
  that samples contain at least one theorem's dependencies.}. This gave $20$
sizes $\times 31$ samples $\times 2$ tools $= 1240$ runs. To keep the total time
down to a few days we chose a timeout of 300 seconds, since that covered most of
the successful QuickSpec and IsaCoSy results we saw, and longer times gave
rapidly diminishing returns.
